The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-07-01 paper.tex
add beam plots

This trade-off can be analyzed quantitatively by trialing several values of $\varepsilon$ and
computing $\|\b v - \b B\b a\|^2$ and $\|\b a\|^2$ for each trial. An example is shown in Figure
\todo{create a figure}. The shape of this curve has a characteristic L-shape, and as a result this
type of plot is called an L-curve \todo{reference}. The ideal value of $\varepsilon$ lies near the
turning point of the plot. At this point a small decrease in $\varepsilon$ will lead to an undesired
rapid increase in $\|\b a\|^2$, and a small increase in $\varepsilon$ will lead to an undesired
rapid increase in $\|\b v - \b B\b a\|^2$.

@@

The antenna complex gains are updated once per day from a 9 hour track of data when Cas A and Cyg A
are at high elevations \todo{the rainy day dataset actually uses a shorter track of data, we should
try using the 9 hour track again}.  These two sources are -- by an order of magnitude -- the
brightest radio sources in the northern hemisphere.  Therefore the optimal time to solve for the
interferometer's gain calibration is when Cas A and Cyg A are at high elevations. A calibration
obtained in this manner is good consistent with the following day's calibration to within a 1\%
error in the flux scale and 1$'$ error in the astrometry \todo{double check these numbers}. These
residual errors are likely driven by differing ionospheric conditions.

@@

In order to generate wide-field images of the sky, the response of the antenna to the sky must be
known. Fortunately drift-scanning interferometers like the OVRO-LWA can empirically measure their
primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
assume that the primary beam is invariant under north-south and east-west flips, and additionally
that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
We measure the flux of several point sources \todo{which ones??} as they pass through the sky and
then fit a beam model composed of Zernike polynomials to those flux measurements. We select the
basis functions to have the desired symmetry.

>>>>

This trade-off can be analyzed quantitatively by trialing several values of $\varepsilon$ and
computing $\|\b v - \b B\b a\|^2$ and $\|\b a\|^2$ for each trial. An example is shown in
Figure~\ref{fig:lcurve}. The shape of this curve has a characteristic L-shape, and as a result this
type of plot is called an L-curve \todo{reference?}. The ideal value of $\varepsilon$ lies near the
turning point of the plot. At this point a small decrease in $\varepsilon$ will lead to an undesired
rapid increase in $\|\b a\|^2$, and a small increase in $\varepsilon$ will lead to an undesired
rapid increase in $\|\b v - \b B\b a\|^2$.

@@

The antenna complex gains are measured from a 7.2 hour track of data from when Cyg A and Cas are at
high elevations. The gains measured in this way are then used to calibrate the entire 28 hour
dataset. Cyg A and Cas A are -- by an order of magnitude -- the brightest point-like radio sources
in the northern hemisphere. Therefore the optimal time to solve for the interferometer's gain
calibration is when these sources are at high elevations. \todo{cite some statistics on how good
this calibration is? what do I quantify?}

\todo{at the moment we calibrated with the Baars spectrum for Cas. we should actually iterate once
and use the new spectrum that comes out of the beam fitting routine}

@@

\begin{figure*}[ht]
    \gridline{
        \fig{figures/beam/source-tracks}{0.45\textwidth}{(a)}
        \fig{figures/beam/stokes-I-beam}{0.45\textwidth}{(b)}
    }
    \caption{
        Example beam model (from spw04).
    }
    \label{fig:beam}
\end{figure*}

In order to generate wide-field images of the sky, the response of the antenna to the sky must be
known. Fortunately drift-scanning interferometers like the OVRO-LWA can empirically measure their
primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
assume that the primary beam is invariant under north-south and east-west flips, and additionally
that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
These symmetries are apparent in the antenna design, but real-world defects and coupling with nearby
antennas will contribute towards breaking these symmetries at some level. However some amount of
symmetry must be assumed in order to break the degeneracy between source flux and beam amplitude
when the flux of a source is unknown.

We measure the flux of several bright sources (Cyg A, Cas A, Tau A, Vir A, Her A, Hya A, Per B, and
3C 353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, $Z_8^8$) and the beam amplitude at
zenith is constrained to be unity.

\todo{plot that shows the tracks after symmetries applied and the resulting beam fit?}
